---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# COVID-19 Incident Risk Assessment Dashboard

<!-- badges: start -->
<!-- badges: end -->

This tool is intended to support line officer and incident
                 manager assessment of COVID-19 risk at the incident level. Updated versions
                 may be provided as both the wildland fire season and our knowledge about COVID
                 changes.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jakedilliott/ciraDash")
```
## Example

To run the shiny app after installing with `devtools::install_github`

```{r example, eval=FALSE}
library(ciraDash) # load the cira package and app
launch_ciraDash() # wrapper function for launching ciraDash
```
